### 2017-06-01 manuscript/usses_water_ms.Rmd
results writing

---
layout: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \linespread{1.25}
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage{sectsty}
  - \usepackage{bm,mathrsfs}
  - \usepackage[sc]{mathpazo}
bibliography: ~/Dropbox/Bibliography/usses_water.bib
csl: components/ecology.csl

@@

\emph{Key words: drought, aboveground net primary productivity, ecosystem stability, climate change, species synchrony, sagebrush steppe}
\end{abstract}

@@

@@

### Data Analysis
We fit generalized linear mixed-effects models (GLMMs) with precipitation, treatment, year, and treatment$\times$year main effects and a random effect for plot.
To account for temporal dependency in the data (i.e., ANPP in 2012 is likely more correlated with ANPP in 2013 than in 2016), we also include an autoregressive error structure [AR(1)].
Thus, our GLMMs account for the fact that each plot is sampled repeatedly over time.
Our models take the form:

\begin{align}
\mu_{i,t} = \textbf{x}_{i,t}\boldsymbol{\beta} + \gamma_i \\
\textbf{y}_{i} \sim \text{MVN}\left(\boldsymbol{\mu}_{i}, \boldsymbol{\Sigma}_i \right) \\
\boldsymbol{\Sigma}_i = \begin{bmatrix}
       \sigma_i^2 & \rho_i\sigma_i^2 & \rho_i^2\sigma_i^2 & \rho_i^3\sigma_i^2 & \rho_i^4\sigma_i^2  \\[0.2em]
       & \sigma_i^2 & \rho_i\sigma_i^2 & \rho_i^2\sigma_i^2 & \rho_i^3\sigma_i^2 \\[0.2em]
       & &  \sigma_i^2 & \rho_i\sigma_i^2 & \rho_i^2\sigma_i^2 \\[0.2em]
       & & & \sigma_i^2 & \rho_i\sigma_i^2 \\[0.2em]
       & & & & \sigma_i^2 \\[0.2em]
     \end{bmatrix}
\end{align}

\noindent{}where $\mu_{i,t}$ is the predicted value of log(ANPP) in plot *i* and year *t*, $\textbf{x}_{i,t}$ is the vector of covariates (including the intercept) associated with plot and year, $\boldsymbol{\beta}$ is the vector of fixed effects associated with each term in $\textbf{x}_{i,t}$, and $\gamma_i$ is the random effect for plot.
We sample the vector of yearly observed log(ANPP) values in each plot ($\textbf{y}_{i}$) from a multivariate normal likelihood with the means from the regression equation (e.g., $\boldsymbol{\mu}_{i}$) and a variance-covariance matrix ($\Sigma_i$) with an AR(1) structure that is unique for each plot.
We fit the above model for the drought and irrigation treatments independently because we are only interested in comparing each treatment to the control, not to eachother.
We fit the model using a Bayesian approach, obtaining posterior estimates of all unkowns via the No-U-Turn Hamiltonian Monte Carlo sampler in Stan [@stan2016].
We used the R package 'rstan' [@rstan2016] to link R to Stan.

@@

Results
-------

>>>>

---
layout: 11pt
header-includes:
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \linespread{1.25}
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage{sectsty}
  - \usepackage{bm,mathrsfs}
  - \usepackage[sc]{mathpazo}
bibliography: ~/Dropbox/Bibliography/usses_water.bib
csl: components/ecology.csl

@@

\emph{Key words: drought, aboveground net primary productivity, ecosystem resistance, climate change, species composition, sagebrush steppe}
\end{abstract}

@@

\linenumbers

@@

### Data Analysis
We fit generalized linear mixed-effects models (GLMMs) with precipitation, treatment, year, and treatment$\times$year main effects and a random effect for plot.
To account for temporal dependency in the data (i.e., ANPP in 2012 is likely more correlated with ANPP in 2013 than in 2016), we also include an autoregressive error structure [AR(1)].
Thus, our GLMMs account for the fact that each plot is sampled repeatedly over time, and that those yearly samples are not independent.
Our models take the form:

\begin{align}
\mu_{i,t} &= \textbf{x}_{i,t}\boldsymbol{\beta} + \gamma_i \\
\textbf{y}_{i} &\sim \text{MVN}\left(\boldsymbol{\mu}_{i}, \boldsymbol{\Sigma}_i \right) \\
\boldsymbol{\Sigma}_i &= \begin{bmatrix}
       1 & \rho_i & \rho_i^2 & \rho_i^3 & \rho_i^4  \\[0.2em]
       & 1 & \rho_i & \rho_i^2 & \rho_i^3 \\[0.2em]
       & &  1 & \rho_i & \rho_i^2 \\[0.2em]
       & & & 1 & \rho_i \\[0.2em]
       & & & & 1 \\[0.2em]
     \end{bmatrix} \sigma_i^2
\end{align}

\noindent{}where $\mu_{i,t}$ is the predicted value of log(ANPP) in plot *i* and year *t*, $\textbf{x}_{i,t}$ is the vector of covariates (including the intercept) associated with plot and year, $\boldsymbol{\beta}$ is the vector of fixed effects associated with each term in $\textbf{x}_{i,t}$, and $\gamma_i$ is the random effect for plot.
We sample the vector of yearly observed log(ANPP) values in each plot ($\textbf{y}_{i}$) from a multivariate normal likelihood with the means from the regression equation (e.g., $\boldsymbol{\mu}_{i}$) and a variance-covariance matrix ($\Sigma_i$) with an AR(1) structure that is unique for each plot.
We fit the above model for the drought and irrigation treatments independently because we are only interested in comparing each treatment to the control, not to eachother.
We fit the model using a Bayesian approach, obtaining posterior estimates of all unkowns via the No-U-Turn Hamiltonian Monte Carlo sampler in Stan [@stan2016].
We used the R package 'rstan' [@rstan2016] to link R [@R2016] to Stan.

@@

All R code and data necessary to reproduce our analysis has been archived on Figshare (\emph{link here after acceptance}) and released on GitHub (https://github.com/atredennick/usses_water/releases/v0.1).
We also include annotated Stan code in our model description in Appendix 1.

Results
-------
Three of our five treatment years fell in years of below average rainfall (Fig. 1A).
Thus, those three years represent a lower magnitude of absolute change in precipitation experienced by the treatments.
Averaged across treatments, ANPP varied from a minimum of xxx g m$^{-2}$ in 2014 to a maximum of xxx g m$^{-2}$ in 2016 (Fig. 1B).
ANPP was slightly higher in irrigation plots and slightly lower in drought plots (Fig. 1B), corresponding to estimated soil volumetric water content (VWC) differences among treatments (Fig. 1C).
Such differences in soil VWC indicate our treatment infrastructure was successful.

Growing season precipitation had a positive effect on ANPP (Fig. 2 and Table 1), but ANPP over the entirety of the experiment was not different from control plots for either drought (Pr(Drought < Control) $\leq$ 0.95) or irrigation (Pr(Irrigation > Control) $\leq$ 0.95) treatments (Fig. 2 and Table 1).
There was also no evidence that the treatment effects became more important over time (Pr(Treatment $\times$ Year) $\leq$ 0.95; Fig. 2B and Table 1).

Community composition was similar among treatments, whether looking at basal cover or density (Fig. 3).
Likewise, community composition was remarkably stable over time, with no evidence of rank shifts or species' declines or gains (Fig. 4).
